%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}

%---------------------------------------------------------
\cvsubsection{Journal Publications}
    \vspace{12pt}
    \begin{cvitems}
    \setlength{\itemsep}{2pt}
    \item{
        \textbf{Libo Wu}{, Zhangjie Chen, and Ya Wang , ``An Adaptive Threshold Approach for Indoor Occupancy Detection with SLEEPIR Sensor Network in Practical Environments'', \textit{will submit to IEEE Sensors Letters}, 2021.}}
     
    \item{
        \textbf{Libo Wu}{ and Ya Wang , ``Study the Characteristics of Polymer Dispersed Liquid Crystal Infrared Shutter on PIR Sensors'', \textit{will submit to IEEE Sensors Journal}, 2021.}}
      
    \item{
        \textbf{Libo Wu}{ and Ya Wang , ``True Occupancy Detection Enabled by the SLEEPIR Sensor and Machine Learning'', \textit{IEEE Sensors Journal}, 2021.}}
      
    \item{
        \textbf{Libo Wu}{, Fangwang Gou, Shin-Tson Wu and Ya Wang , ``SLEEPIR: Synchronized Low-Energy Electronically-Chopped PIR Sensor for True Presence Detection'', \textit{IEEE Sensors Letters}, 4(3), pp. 1-4, 2020.}}
        
    \item{
        \textbf{Libo Wu}{, and Ya Wang, ``Compressive Sensing Based Indoor Occupancy Positioning Using A Single Thermopile Point Detector with a Coded Binary Mask'', \textit{IEEE Sensors Letters}, 3(12), pp. 1-4, 2019.}}
  
    \item{
        \textbf{Libo Wu}{, Ya Wang and Haili Liu, ``Detection and Localization of Individuals by Monitoring Nonlinear Energy Flow of a Shuttered Passive Infrared Sensor'', \textit{IEEE Sensors Journal}, 18(21), pp. 8656-8666, 2018.}}
  
    \item{
        \textbf{Libo Wu}{ and Ya Wang, ``A Low Power Electric-Mechanical Driving Approach for True Occupancy Detection Using a Shuttered Passive Infrared Sensor'', \textit{IEEE Sensors Journal}, 19(1), pp. 47-57, 2018.}}
    \end{cvitems}
    \vspace{12pt}


%---------------------------------------------------------
\cvsubsection{Conference Proceedings}
\vspace{12pt}
\begin{cvitems}
    \setlength{\itemsep}{2pt}
      \item{
        \textbf{Libo Wu}{ and Ya Wang, ``True Presence Detection via Passive Infrared Sensor Network Using Liquid Crystal Infrared Shutters'', \textit{ASME SMASIS conference, 2020.}}}
      
      \item{
        \textbf{Libo Wu}{ and Ya Wang, ``Compressive Sensing Based Indoor Human Positioning Using A Single Thermopile Point Detector'', \textit{12th International Workshop on Structural Health Monitoring, September 10-12, 2019, Stanford, California, USA.}}}
      
      \item{
        \textbf{Libo Wu}{ and Ya Wang, ``Shuttered Passive Infrared Sensor for Occupancy Detection: Exploring A Low Power Electro-Mechanical Driving Approach'', \textit{ASME SMASIS conference}, 2018 (Oral presentation).}}    
      \end{cvitems}
      \vspace{8pt}

    
\end{cvparagraph}
